Multisensor Architecture for an Intersection Management System

### 2015-06-10 ch2-mdf_ims.tex
Semi-Finished chapter 2

>>>>

Although many works based on cameras are found, there are two main developments that make use of range sensors along cameras to implement an IMS. The first one, developed by POSS research group at Peking University\footnote{http://www.poss.pku.edu.cn/index.html}, is the POSSi project which main objective is monitoring a dynamic environment through fusion of laser and video. In this project, a set of laser scanners are deployed on corners of an intersection and a camera is installed over a pedestrian bridge. They perform a fusion over laser data and after detection and recognition of vehicles and pedstrians, this info is backprojected on video stream.

The second relevant project, Ko-PER project\footnote{http://ko-fas.de/english/ko-per---cooperative-perception.html}, was developed by the Institute of Measurement, Control and Microtechnology at Ulm University under Ko-FAS research initiative. Ko-PER project aims to capture a complete picure of the local traffic environment. In order to do so, a full deployment of infrastructure was made, using 14 laserscanners, 10 cameras, a GPS and a V2I communication unit. Also, they perform a low-level fusion over same type sensor first, and then they merge outputs of each subsystem for improve detection and analysis results.

In the proposed work, there is not a deployment of sensors in an intersection scenario, but datasets from the previous mentioned projects will be used instead. Also, one of the objectives is to explore and propose a modular fusion architecture/framework for IMS based on cameras and laser sensors. In table X a summary of aforementioned developments is presented, including proposed work.

\begin{table}
\begin{tabular}{|c|c|p{0.125\linewidth}|p{0.15\linewidth}|c|c|c|c|}
\hline

\textbf{References} & \textbf{Project} & \textbf{Sensors} & \textbf{Target} & \textbf{Fusion} & \textbf{Framework} \\
\hline

\cite{Zhao2006} & POSSi & Laser & Vehicles, pedestrians & No & No \\
\hline

\cite{Song2008} & POSSi & Lasers & Pedestrians & Yes & No \\
\hline

\cite{Zhao2008} & POSSi & Lasers & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Zhao2009} & POSSi & Lasers, Camera & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Zhao2012} & POSSi & Lasers & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Goldhammer2012} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Meissner2012} & Ko-PER & Lasers & Pedestrians & Yes & No \\
\hline

\cite{Meissner2013} & Ko-PER & Lasers & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Meissner2013a, Meissner2013b} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
\hline

\cite{Strigel2013} & Ko-PER & Cameras & Vehicles & Yes & No \\
\hline

\cite{Meissner2014} & Ko-PER & Lasers, Cameras & Vehicles, pedestrians & Yes & No \\
\hline

%\cite{} &  &  &  &  &  \\
%\hline

Proposed work & - & Lasers, Cameras & Vehicles & Multilevel & Yes \\
\hline

\end{tabular}
\end{table}
